Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-18 paper/main.tex
I am confused

% group AV
On a group-average level, results for the audio-visual movie show significantly
increased hemodynamic activity spatially overlapping with a conventionally
localized PPA, but also extending into earlier visual cortices.
% group AD
Likewise, results for the audio-description identify significant activation in
the PPA but restricted to its anterior part.
% individual level
Moroever, the group averages are representative for the majority of individual
results, where, for example, the audio-description stimulus yields bilateral
clusters in the anterior PPA of nine participants and a unilateral cluster in
one participant.
% meaning: generalization to naturalistic stimuli
These findings suggest that increased activation in the PPA during the
perception of static pictures generalizes to the perception of spatial
information embedded in a movie or a purely auditory narrative.
% narrative as substitute
The presented evidence on the in-principle suitability of an auditory-only
paradigm for localizing the PPA may offer a path to the development of
diagnostic procedures more suitable for populations of individuals with visual
impairments or conditions like nystagmus.
% meaning: aPPA vs. pPPA
Our results provide further evidence that the PPA can be divided into functional
subregions \citep{aminoff2007parahippocampal, aminoff2015associative,
baldassano2013differential, baldassano2016two, baumann2016functional}.

>>>>

% group AV
On a group-average level, results for the audio-visual movie show significantly
increased hemodynamic activity spatially overlapping with a conventionally
localized PPA but also extending into earlier visual cortices.
% group AD
Likewise, results for the audio-description identify significant activation in
the PPA but restricted to its anterior part.
% individual level
Moroever, the group averages are representative for the majority of individual
results, where, for example, the audio-description stimulus yields bilateral
clusters in the anterior PPA of nine participants and a unilateral cluster in
one participant.
% meaning: generalization to naturalistic stimuli
These findings suggest that increased activation in the PPA during the
perception of static pictures generalizes to the perception of spatial
information embedded in a movie or a purely auditory narrative.
% narrative as substitute
The presented evidence on the in-principle suitability of a purely auditory
paradigm for localizing the PPA may offer a path to the development of
diagnostic procedures more suitable for individuals with visual impairments or
conditions like nystagmus.
% meaning: aPPA vs. pPPA
Our results provide further evidence that the PPA can be divided into functional
subregions \citep{aminoff2007parahippocampal, aminoff2015associative,
baldassano2013differential, baldassano2016two,
baumann2016functional}.\todo{claim hängt hier etwas in der Luft; wird später
ausführlicher diskutiert}
